Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-01-18 Multiresolution_framework/ltx/manuscript.tex
more edtis to MRA SS section - I think it is ok now for general scenario

\section{IDE Neural Field Model}
The stochastic IDE form of the Amari neural field  formulation~\cite{Amari1977} is given by (see~\cite{Freestone2011} for a full derivation)
\begin{equation}\label{eq:DiscreteTimeModel}
	v_{t+1}\left(\mathbf{r}\right) = 
	\xi v_t\left(\mathbf{r}\right) + 
	T_s \int_\Omega { 
	    w\left(\mathbf{r},\mathbf{r'}\right)
	    f\left(v_t\left(\mathbf{r}'\right)\right) 
	\, d\mathbf{r}'} 
	+ e_t\left(\mathbf{r}\right), 
\end{equation}
where the post-synaptic membrane voltage at time $t$ of a population of neurons at position $\mathbf r$ is denoted $v_t\left(\mathbf r\right)$. Membrane dynamics are included through the parameter $\xi=1-T_s/\tau$, where $\tau$ is the membrane time constant and $T_s$ is the sampling time. The connectivity strength between neural populations at a distance $\mid\mathbf{r}-\mathbf{r'}\mid$ is described by the connectivity kernel $w\left(\mathbf{r}-\mathbf{r}'\right)$. The connectivity kernel is taken as a ``Mexican hat'' function, which describes local excitation and lateral inhibition \cite{Amari1977,Atay2005}. The term $e_t(\mathbf r)$ is a zero mean Gaussian disturbance, spatially coloured but temporally white, with covariance function 
\begin{equation}
cov\left(e_{t}\left(\mathbf{r}\right),e_{t+t'}\left(\mathbf{r'}\right)\right)=\eta(\mathbf{r}-\mathbf{r'})\delta(t-t'),
\label{eq:FieldDisturbance}
\end{equation}
where $\delta(\cdot)$ is the Dirac-delta function. The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})$ \cite{VanRotterdam1982,Murphy2009}.

The observation equation describing the intracranial electrophysiological recordings is given by
\begin{equation}\label{eq:ObservationEquation}
	y_t(\mathbf{r}_{n_y}) = \int_{\Omega} { m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, d\mathbf{r}'} + \boldsymbol\epsilon_t(\mathbf{r}_{n_y}), 
\end{equation}
where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel at location $\mathbf{r}_{n_y}$ and  $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$  is an i.i.d. Gaussian white noise process and the covariance matrix $\mathbf{\Sigma}_{\epsilon}=\sigma^2_{\epsilon}\mathbf I_{n_y}$, where $\mathbf I$ denotes the identity matrix.

@@

% where the unknown parameter and state vectors, $\boldsymbol\theta \in \mathbb{R}^{n_{\theta}}$ and $\mathbf{x}_t \in \mathbb{R}^{n_x}$, \dean{($\boldsymbol\theta \in \mathbb{R}^{n_{\theta}\times (J+2)}$ and $\mathbf{x}_t \in \mathbb{R}^{n_x \times (J+2)}$)} are defined as 
% \begin{align}
% \boldsymbol\theta^\top \triangleq& [\begin{array}{ccccc} \boldsymbol\alpha_{j_0}^\top & \boldsymbol\beta_{j_0}^\top & \boldsymbol\beta_{j_0+1}^\top & \cdots & \boldsymbol\beta_{J}^\top \end{array}] 
% \label{KernelWeights} \\
% \mathbf{x}_{t}^\top \triangleq& [\begin{array}{ccccc}\mathbf{x}_{t,j_{0}}^\top &  \check{\mathbf{x}}_{t,j_{0}}^\top & \check{\mathbf{x}}_{t,j_{0}+1}^\top & \cdots & \check{\mathbf{x}}_{t,J}^\top\end{array}].
% \label{FieldWeights}
% \end{align}
% The kernel and field approximation coefficient vectors, $\boldsymbol \alpha_{j_0}$ and $\mathbf{x}_{t,j_{0}}$, contain all the coefficients $\left\lbrace\alpha_{j_0, \mathbf{l}}:\mathbf{l} \in \mathbb{Z}^n \right\rbrace $ and $\left\lbrace x_{t,j_0, \mathbf{l}}: \mathbf{l} \in \mathbb{Z}^n\right\rbrace$, respectively. Similarly, the kernel and the field detail coefficient vectors, $\boldsymbol\beta_{j}$ and $\check{\mathbf{x}}_{t,j}$, contain all the coefficients $\left\lbrace \beta_{j,\mathbf{l}} :\mathbf{l} \in \mathbb{Z}^n\right\rbrace$ and $\left\lbrace  \check x_{t,j,\mathbf{l}}:\mathbf{l} \in \mathbb{Z}^n\right\rbrace$, respectively.
% 
% The vectors of the kernel and the field scaling and wavelet functions, $\boldsymbol\lambda$ and $\boldsymbol\mu$, respectively, are defined by
% \begin{align}
%     \label{KernelBasisVector}
%     \boldsymbol\lambda^\top(\mathbf{r}) \triangleq& \left[
%     \begin{array}{ccccc} \boldsymbol\phi_{j_0}^\top(\mathbf{r}) &
%     \boldsymbol\psi_{j_0}^\top(\mathbf{r}) & 
%     \boldsymbol\psi_{j_0+1}^\top(\mathbf{r}) &
%     \cdots &
%     \boldsymbol\psi_{J}^\top(\mathbf{r})\end{array}\right] \\
%     \label{FieldBasisVector}
%     \boldsymbol\mu^\top (\mathbf{r}) \triangleq& \left[
%     \begin{array}{ccccc}\boldsymbol\phi_{j_0}^\top(\mathbf{r}) &
%     \boldsymbol\psi_{j_0}^\top(\mathbf{r}) & 
%     \boldsymbol\psi_{j_0+1}^\top(\mathbf{r}) &
%     \cdots &
%     \boldsymbol\psi_{J}^\top(\mathbf{r})\end{array}\right]
% \end{align}
% 
% The vectors in  (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in  (\ref{KernelWeights}) and (\ref{FieldWeights}).  
Now we have the compact for of the decomposition we can substitute this into the neural field equation \eqref{eq:DiscreteTimeModel} giving
\begin{equation}\label{eq:DiscreteTimeModel}
	\boldsymbol\mu^\top\left(\mathbf{r}\right)\mathbf{x}_t = 
	\xi \boldsymbol\mu^\top\left(\mathbf{r}\right)\mathbf{x}_t + 
	T_s \int_\Omega { 
	    \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}-\mathbf{r}'\right)
	    f\left(\boldsymbol\mu^\top\left(\mathbf{r}'\right)\mathbf{x}_t\right) 
	\, \mathrm{d}\mathbf{r}'}  
	+ e_t\left(\mathbf{r}\right), 
\end{equation}

To derive the state-space model, we first define the matrices 
\begin{align}\label{eq:Lambdax}
 \mathbf{\Lambda}_{x} &\triangleq \int_{\Omega}\boldsymbol\mu\left(r\right)\boldsymbol\mu^\top\left(r\right) dr \\
\label{eq:Lambdatheta}
 \mathbf{\Lambda}_{\theta} &\triangleq \int_{\Omega}\boldsymbol\mu\left(r\right) \int_\Omega { 
	   \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
	    \boldsymbol\mu^\top\left(r\right)\ dr'dr.}
\end{align}
Substituting \eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} in \eqref{eq:DiscreteTimeModel}, pre-multiplying by $\boldsymbol\mu\left(r\right)$, and integrating over the space gives
\begin{align}\label{eq:DecomposedModel2} 
	&\mathbf{\Lambda}_{x} \mathbf{x}_{t+1} = 
	\xi\mathbf{\Lambda}_{x} \mathbf{x}_t +T_s \varsigma \mathbf{\Lambda}_{\theta}\mathbf{x}_t +\int_{\Omega}\boldsymbol\mu\left(r\right)e_t\left(r\right)dr.
\end{align}
Cross-multiplying by $\mathbf{\Lambda}_{x}^{-1}$ gives the state transition equation
\begin{align}\label{eq:StateEquation}
 \mathbf x_{t+1} &=\mathbf A(\boldsymbol \theta) \mathbf x_t+ \mathbf w_t\\
\label{eq:A_theta}
 \mathbf A(\boldsymbol \theta) &= T_s\varsigma\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I.
\end{align}
The disturbance becomes 
\begin{equation}\label{eq:Disturbance}
\mathbf w_t= \mathbf{\Lambda}_{x}^{-1}\int_{\Omega}\boldsymbol\mu \left(r\right)e_t\left(r\right)dr,
\end{equation}
which is a vector valued, zero-mean normally distributed, white noise process with covariance (see \cite{Freestone2011} for proof)
\begin{equation}\label{eq:CovMatrix}
\boldsymbol\Sigma_w =\mathbf{\Lambda}_{x}^{-1}\iint\limits_{\boldsymbol\Omega}\boldsymbol\mu\left(r\right) \eta\left(r-r'\right)\boldsymbol\mu^{\top}\left(r'\right)dr'dr\mathbf{\Lambda}_{x}^{-\top}.
\end{equation}
The observation equation of the state-space model is found by substituting decomposition \eqref{eq:FieldFiniteExpansion}
 into \eqref{eq:ObservationEquation} giving
\begin{equation}\label{eq:ReducedObservationEquation} 
	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
\end{equation}
where each element of the observation matrix is given by
\begin{equation}\label{eq:Observationmatrix}
	\mathbf{C}_{ij} \triangleq \int_{\Omega}m(r_i - r')\boldsymbol{\mu}_j(r') \, d\mathbf{r}'.
\end{equation}
\section{B-spline MRAIDE in State-Space }
B-spline functions are one of the most basic elements for wavelet construction, these functions are composed of  piecewise polynomials combined smoothly at some breaking points (knots) which are equally spaced in the case of cardinal B-splines. The degree of smoothness is determined by the order of splines \cite{Goswami1999} where the higher the order, the smoother the resulting B-spline becomes (see Figure~\ref{fig:Figure0}).
\begin{figure}[!ht]
\centering
\includegraphics{./Graph/Figure0.pdf}
% \includegraphics{./Graph/Figure0b.pdf}
\caption{{\bf Examples of cardinal B-spline functions}. Piecewise polynomial functions (coloured lines) are joined at the break points (black dots). (\textbf{A}) B-spline function of order 2 (linear B-spline). (\textbf{B}) B-spline function of order 8.}
\label{fig:Figure0}
\end{figure}

>>>>

\section{IDE Neural Field Model}
The stochastic IDE form of the Amari neural field  formulation~\cite{Amari1977} is given by (see~\cite{Freestone2011} for a full derivation)
\begin{equation}\label{eq:DiscreteTimeModel}
	v_{t+1}\left(\mathbf{r}\right) = 
	\xi v_t\left(\mathbf{r}\right) + 
	T_s \int_\Omega { 
	    w\left(\mathbf{r},\mathbf{r'}\right)
	    f\left(v_t\left(\mathbf{r}'\right)\right) 
	\, \mathrm{d}\mathbf{r}'} 
	+ e_t\left(\mathbf{r}\right), 
\end{equation}
where the post-synaptic membrane voltage at time $t$ of a population of neurons at position $\mathbf r$ is denoted $v_t\left(\mathbf r\right)$. Membrane dynamics are included through the parameter $\xi=1-T_s/\tau$, where $\tau$ is the membrane time constant and $T_s$ is the sampling time. The connectivity strength between neural populations at a distance $\mid\mathbf{r}-\mathbf{r'}\mid$ is described by the connectivity kernel $w\left(\mathbf{r}-\mathbf{r}'\right)$. The connectivity kernel is taken as a ``Mexican hat'' function, which describes local excitation and lateral inhibition \cite{Amari1977,Atay2005}. The term $e_t(\mathbf r)$ is a zero mean Gaussian disturbance, spatially coloured but temporally white, with covariance function 
\begin{equation}
cov\left(e_{t}\left(\mathbf{r}\right),e_{t+t'}\left(\mathbf{r'}\right)\right)=\eta(\mathbf{r}-\mathbf{r'})\delta(t-t'),
\label{eq:FieldDisturbance}
\end{equation}
where $\delta(\cdot)$ is the Dirac-delta function. The firing rate of the presynaptic neurons is related to the post-synaptic membrane potential by the activation function $f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r})$ \cite{VanRotterdam1982,Murphy2009}.

The observation equation describing the intracranial electrophysiological recordings is given by
\begin{equation}\label{eq:ObservationEquation}
	y_t(\mathbf{r}_{n_y}) = \int_{\Omega} { m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, \mathrm{d}\mathbf{r}'} + \boldsymbol\epsilon_t(\mathbf{r}_{n_y}), 
\end{equation}
where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel at location $\mathbf{r}_{n_y}$ and  $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$  is an i.i.d. Gaussian white noise process and the covariance matrix $\mathbf{\Sigma}_{\epsilon}=\sigma^2_{\epsilon}\mathbf I_{n_y}$, where $\mathbf I$ denotes the identity matrix.

@@

% where the unknown parameter and state vectors, $\boldsymbol\theta \in \mathbb{R}^{n_{\theta}}$ and $\mathbf{x}_t \in \mathbb{R}^{n_x}$, \dean{($\boldsymbol\theta \in \mathbb{R}^{n_{\theta}\times (J+2)}$ and $\mathbf{x}_t \in \mathbb{R}^{n_x \times (J+2)}$)} are defined as 
% \begin{align}
% \boldsymbol\theta^\top \triangleq& [\begin{array}{ccccc} \boldsymbol\alpha_{j_0}^\top & \boldsymbol\beta_{j_0}^\top & \boldsymbol\beta_{j_0+1}^\top & \cdots & \boldsymbol\beta_{J}^\top \end{array}] 
% \label{KernelWeights} \\
% \mathbf{x}_{t}^\top \triangleq& [\begin{array}{ccccc}\mathbf{x}_{t,j_{0}}^\top &  \check{\mathbf{x}}_{t,j_{0}}^\top & \check{\mathbf{x}}_{t,j_{0}+1}^\top & \cdots & \check{\mathbf{x}}_{t,J}^\top\end{array}].
% \label{FieldWeights}
% \end{align}
% The kernel and field approximation coefficient vectors, $\boldsymbol \alpha_{j_0}$ and $\mathbf{x}_{t,j_{0}}$, contain all the coefficients $\left\lbrace\alpha_{j_0, \mathbf{l}}:\mathbf{l} \in \mathbb{Z}^n \right\rbrace $ and $\left\lbrace x_{t,j_0, \mathbf{l}}: \mathbf{l} \in \mathbb{Z}^n\right\rbrace$, respectively. Similarly, the kernel and the field detail coefficient vectors, $\boldsymbol\beta_{j}$ and $\check{\mathbf{x}}_{t,j}$, contain all the coefficients $\left\lbrace \beta_{j,\mathbf{l}} :\mathbf{l} \in \mathbb{Z}^n\right\rbrace$ and $\left\lbrace  \check x_{t,j,\mathbf{l}}:\mathbf{l} \in \mathbb{Z}^n\right\rbrace$, respectively.
% 
% The vectors of the kernel and the field scaling and wavelet functions, $\boldsymbol\lambda$ and $\boldsymbol\mu$, respectively, are defined by
% \begin{align}
%     \label{KernelBasisVector}
%     \boldsymbol\lambda^\top(\mathbf{r}) \triangleq& \left[
%     \begin{array}{ccccc} \boldsymbol\phi_{j_0}^\top(\mathbf{r}) &
%     \boldsymbol\psi_{j_0}^\top(\mathbf{r}) & 
%     \boldsymbol\psi_{j_0+1}^\top(\mathbf{r}) &
%     \cdots &
%     \boldsymbol\psi_{J}^\top(\mathbf{r})\end{array}\right] \\
%     \label{FieldBasisVector}
%     \boldsymbol\mu^\top (\mathbf{r}) \triangleq& \left[
%     \begin{array}{ccccc}\boldsymbol\phi_{j_0}^\top(\mathbf{r}) &
%     \boldsymbol\psi_{j_0}^\top(\mathbf{r}) & 
%     \boldsymbol\psi_{j_0+1}^\top(\mathbf{r}) &
%     \cdots &
%     \boldsymbol\psi_{J}^\top(\mathbf{r})\end{array}\right]
% \end{align}
% 
% The vectors in  (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in  (\ref{KernelWeights}) and (\ref{FieldWeights}).  
Now we have the compact for of the decomposition we can substitute this into the neural field equation \eqref{eq:DiscreteTimeModel} giving
\begin{equation}\label{eq:ApproxDiscreteTimeModel}
	\boldsymbol\mu^\top\left(\mathbf{r}\right)\mathbf{x}_{t+1} = 
	\xi \boldsymbol\mu^\top\left(\mathbf{r}\right)\mathbf{x}_t + 
	T_s \int_\Omega { 
	    \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}-\mathbf{r}'\right)
	    f\left(\boldsymbol\mu^\top\left(\mathbf{r}'\right)\mathbf{x}_t\right) 
	\, \mathrm{d}\mathbf{r}'}  
	+ e_t\left(\mathbf{r}\right).
The aim of the next part of the derivation is to isolate the state vector on the left hand side of the equation. To do this we first multiply both sides of equation~\eqref{eq:ApproxDiscreteTimeModel} by $\boldsymbol\mu\left(r\right)$ and integrate over space giving 
\begin{equation}\label{eq:ApproxDiscreteTimeModel2}
	\int_{\Omega} \boldsymbol\mu\left(\mathbf{r}\right)\boldsymbol\mu^\top\left(\mathbf{r}\right) \mathrm{d}\mathbf{r} \mathbf{x}_{t+1} = 
	\xi \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)\boldsymbol\mu^\top\left(\mathbf{r}\right) \mathrm{d}\mathbf{r} \mathbf{x}_t + 
	T_s \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)\int_\Omega { 
	    \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}-\mathbf{r}'\right)
	    f\left(\boldsymbol\mu^\top\left(\mathbf{r}'\right)\mathbf{x}_t\right) 
	\, \mathrm{d}\mathbf{r}'\mathrm{d}\mathbf{r}}  
	+ \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)\mathrm{d}\mathbf{r}.
To isolate the state vector, we now define the matrix 
	\label{eq:Lambdax}
	 \mathbf{\Lambda}_{x} \triangleq \int_{\Omega}\boldsymbol{\mu}\left(\mathbf{r}\right)\boldsymbol{\mu}^\top\left(\mathbf{r}\right) \mathrm{d}\mathbf{r}
and substitute into equation~\eqref{eq:ApproxDiscreteTimeModel2} giving
\begin{equation}\label{eq:ApproxDiscreteTimeModel3}
	\mathbf{\Lambda}_{x} \mathbf{x}_{t+1} = 
	\xi \mathbf{\Lambda}_{x} \mathbf{x}_t + 
	T_s \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)\int_\Omega { 
	    \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}-\mathbf{r}'\right)
	    f\left(\boldsymbol\mu^\top\left(\mathbf{r}'\right)\mathbf{x}_t\right) 
	\, \mathrm{d}\mathbf{r}'\mathrm{d}\mathbf{r}}  
	+ \int_{\Omega}\boldsymbol{\mu}\left(\mathbf{r}\right) e_t\left(\mathbf{r}\right) \mathrm{d}\mathbf{r}.
Cross-multiplying by $\mathbf{\Lambda}_{x}^{-1}$ gives the state transition equation
\begin{equation}\label{eq:ApproxDiscreteTimeModel4}
	\mathbf{x}_{t+1} = 
	\xi \mathbf{x}_t + 
	T_s \mathbf{\Lambda}_{x}^{-1} \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)\int_\Omega { 
	    \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}-\mathbf{r}'\right)
	    f\left(\boldsymbol\mu^\top\left(\mathbf{r}'\right)\mathbf{x}_t\right) 
	\, \mathrm{d}\mathbf{r}'\mathrm{d}\mathbf{r}}  
	+ \mathbf{\Lambda}_{x}^{-1}\int_{\Omega}\boldsymbol{\mu}\left(\mathbf{r}\right) e_t\left(\mathbf{r}\right) \mathrm{d}\mathbf{r}.
A very nice property of the MRAIDE framework is the the disturbance term becomes a vector valued, zero-mean normally distributed, white noise process 
\begin{equation}\label{eq:Disturbance}
\mathbf w_t= \mathbf{\Lambda}_{x}^{-1}\int_{\Omega}\boldsymbol\mu \left(\mathbf{r}\right)e_t\left(\mathbf{r}\right)\,\mathrm{d}\mathbf{r},
with covariance (see \cite{Freestone2011} for proof)
\begin{equation}\label{eq:CovMatrix}
\boldsymbol\Sigma_w =\mathbf{\Lambda}_{x}^{-1}\iint\limits_{\boldsymbol\Omega}\boldsymbol\mu\left(\mathbf{r}\right) \eta\left(\mathbf{r}-\mathbf{r}'\right)\boldsymbol\mu^{\top}\left(\mathbf{r}'\right)\,\mathrm{d}\mathbf{r}'\mathrm{d}\mathbf{r}\mathbf{\Lambda}_{x}^{-\top}.
% \begin{align}\label{eq:Lambdax}
%  \mathbf{\Lambda}_{x} &\triangleq \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)\boldsymbol\mu^\top\left(\mathbf{r}\right) \mathrm{d}\mathbf{r} \\
% \label{eq:Lambdatheta}
%  \mathbf{\Lambda}_{\theta} &\triangleq \int_{\Omega}\boldsymbol\mu\left(r\right) \int_\Omega { 
% 	   \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
% 	    \boldsymbol\mu^\top\left(r\right)\ dr'dr.}
% \end{align}
% Substituting \eqref{eq:KernelFiniteExpansion} and \eqref{eq:FieldFiniteExpansion} in \eqref{eq:DiscreteTimeModel}, pre-multiplying by $\boldsymbol\mu\left(r\right)$, and integrating over the space gives
% \begin{align}\label{eq:DecomposedModel2} 
% 	&\mathbf{\Lambda}_{x} \mathbf{x}_{t+1} = 
% 	\xi\mathbf{\Lambda}_{x} \mathbf{x}_t +T_s \varsigma \mathbf{\Lambda}_{\theta}\mathbf{x}_t +\int_{\Omega}\boldsymbol\mu\left(r\right)e_t\left(r\right)dr.
% \end{align}
% Cross-multiplying by $\mathbf{\Lambda}_{x}^{-1}$ gives the state transition equation
% \begin{align}\label{eq:StateEquation}
%  \mathbf x_{t+1} &=\mathbf A(\boldsymbol \theta) \mathbf x_t+ \mathbf w_t\\
% \label{eq:A_theta}
%  \mathbf A(\boldsymbol \theta) &= T_s\varsigma\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I.
% \end{align}
% The disturbance becomes 
% \begin{equation}\label{eq:Disturbance}
% \mathbf w_t= \mathbf{\Lambda}_{x}^{-1}\int_{\Omega}\boldsymbol\mu \left(r\right)e_t\left(r\right)dr,
% \end{equation}
% which is a vector valued, zero-mean normally distributed, white noise process with covariance (see \cite{Freestone2011} for proof)
% \begin{equation}\label{eq:CovMatrix}
% \boldsymbol\Sigma_w =\mathbf{\Lambda}_{x}^{-1}\iint\limits_{\boldsymbol\Omega}\boldsymbol\mu\left(r\right) \eta\left(r-r'\right)\boldsymbol\mu^{\top}\left(r'\right)dr'dr\mathbf{\Lambda}_{x}^{-\top}.
% \end{equation}

The observation equation of the state-space model is found by substituting decomposition \eqref{eq:FieldFiniteExpansion}
 into \eqref{eq:ObservationEquation} giving
\begin{equation}\label{eq:ReducedObservationEquation} 
	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
\end{equation}
where each element of the observation matrix, $\mathbf{C}$, is given by
\begin{equation}\label{eq:Observationmatrix}
	\mathbf{C}_{ik} \triangleq \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\mu}_k(\mathbf{r}') \, \mathrm{d}\mathbf{r}'.
\end{equation}

\section{B-spline MRAIDE in State-Space }
B-spline functions are one of the most basic elements for wavelet construction. These functions are composed of  piecewise polynomials combined smoothly at some breaking points (knots) which are equally spaced in the case of cardinal B-splines. The degree of smoothness is determined by the order of splines \cite{Goswami1999} where the higher the order, the smoother the resulting B-spline becomes (see Figure~\ref{fig:Figure0}).
\begin{figure}[!ht]
\centering
\includegraphics{./Graph/Figure0.pdf}
% \includegraphics{./Graph/Figure0b.pdf}
\caption{{\bf Examples of cardinal B-spline functions}. Piecewise polynomial functions (coloured lines) are joined at the break points (black dots). (\textbf{A}) B-spline function of order 2 (linear B-spline). (\textbf{B}) B-spline function of order 8.}
\label{fig:Figure0}
\end{figure}
